Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-03 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations from literature
Latest draft (many tweaks (esp starting slides)

% Color scheme
\definecolor{cerulean}{rgb}{0.16, 0.32, 0.75}
\definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
\definecolor{offwhite}{RGB}{255,253,243}
\definecolor{red}{RGB}{213,94,0}
%#09BADB #DB1A71

@@

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
\setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
%\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}
\setbeamerfont{button}{size={\fontsize{8}{8}}}
\linespread{1.25}

@@

\subsection{Business Practices Around the World}

\begin{frame}
\frametitle{Business Practices in Large Companies}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices in Large Companies}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010, Bloom2016, Bloom2019}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in Small Firms}

	\citet{McKenzie2017} develop measurement instrument of \textcolor{bdf}{26 business practices} 
	\begin{itemize_2pt}
		\item Administered in \textcolor{bdf}{7 countries} in Asia, Africa, and South America

@@

		\item 4 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices in Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g.,  
		\end{enumerate_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices in Small Firms}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
	\label{McKenzie(2017): Heterogeneity}
\end{figure}

\begin{itemize_2pt}
	\item Hetereogeneity in business practices of MSEs across countries \citep{McKenzie2017}
\end{itemize_2pt}
\end{frame}

@@

		\begin{itemize_2pt}
			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
			\item[] .. where $\textcolor{red}{p}$ is the output price, $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, and $\textcolor{red}{r}$ cost of capital
			\item[] .. where $\textcolor{red}{A}$ represents a productivity factor and \textcolor{red}{$\lambda$} parameterizes borrowing constraints
		\end{itemize_2pt}

@@

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology boosting productivity factor $\textcolor{red}{A}$
			\item[] \citep[see,][]{Bloom2016, McKenzie2017}
		\end{enumerate_2pt}

	%\item Bloom et al. (2016) Bloom N, Sadun R, Van Reenen J (2016) Management as a technol- ogy? NBERWorking Paper 22327, National Bureau of Economic Research, Cambridge, MA.
	%\item McKenzie2017 3.1.
	\end{itemize_2pt}

@@

Further potential channels of impact
\begin{enumerate_2pt}
	\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013} %Bruhn JDEff 2013 Stimulating managerial capital young entrepreneurs Bosnia
	\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand

	\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth
	\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
\end{enumerate_2pt}

@@

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
	\item McKenzie2017: \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity

@@

@@

	Including more recent evaluations \citep[see,][]{McKenzie2020}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
		\item More severe constraints, e.g., due to household-level reallocation \citep{Bernhardt2019, deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

Typical Consulting Intervention
\begin{itemize_2pt}
	\item Three-step procedure
	\begin{enumerate_2pt}
		\item Diagnostic of practices
		\item Identification of areas of improvement
		\item Problem solving within interactive relationship
	\end{enumerate_2pt}

@@

	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically around 10\%)
	\begin{itemize_2pt}
		\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
	\end{itemize_2pt}

@@

@@

\subsection{Measurement of Firm Performance}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=23.5em]{pics/McK2020_profits.png}
		\label{McKenzie(2020): Profits}
	\end{figure}

@@

	\begin{itemize_2pt}
		\item \textcolor{bdf}{Extremely wide confidence intervals} on impact estimates
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\appendix
\begin{frame}[label=references, allowframebreaks]
\frametitle{References}
\bibliographystyle{econometrica}
\bibliography{SME_library}
\end{frame}

>>>>

% Color scheme
\definecolor{cerulean}{rgb}{0.16, 0.32, 0.75}
\definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
\definecolor{offwhite}{RGB}{255,253,243}
\definecolor{red}{RGB}{213,94,0}
\definecolor{camel}{rgb}{0.76, 0.6, 0.42}
%#09BADB #DB1A71

@@

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
\setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
\setbeamerfont{itemize/enumerate subsubbody}{size={\fontsize{7}{7}}}
%\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}
\setbeamerfont{button}{size={\fontsize{8}{8}}}
\linespread{1.25}

\hypersetup{
	colorlinks,
    linkcolor= black, % internal links
    citecolor= camel, % citations
    urlcolor= black % external links/urls
}

@@

\subsection{Business Practices and Productivity}

\begin{frame}
\frametitle{Dispersion of Business Practices}

Stylized facts about firms
\begin{table}[ht]
\small
\begin{center}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
Large \textcolor{cerulean}{country-level} 	& Large \textcolor{cerulean}{country-level} 	\\
heterogeneity 			& heterogeneity 		\\
in \textcolor{bdf}{productivity} 		& in \textcolor{bdf}{mgmt quality}	 	\\
\hline
Large \textcolor{cerulean}{firm-level} 		& Large \textcolor{cerulean}{firm-level} 		\\
heterogeneity			& heterogeneity 		\\
in \textcolor{bdf}{productivity}      	& in \textcolor{bdf}{mgmt quality} \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{frame}
\frametitle{Dispersion of Business Practices}

Mid-sized and large companies

\begin{figure}[htbp]
	\centering
	\includegraphics[width=17.4em]{pics/Bloom2010_mgmtdispersion.png}
	\label{Bloom(2010): Mgmt practices}
\end{figure}

\vspace{-1.0em}

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \citep{Bloom2007, Bloom2010, Syverson2011}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Dispersion of Business Practices}

Public-sector companies

\begin{figure}[htbp]
	\centering
	\includegraphics[width=17.4em]{pics/Bloom2015_mgmtdispersion.png}
	\label{Bloom(2015): Mgmt practices}
\end{figure}

\vspace{-1.0em}

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across schools \citep{Bloom2015} and hospitals \citep{Bloom2020}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Dispersion of Business Practices}

Small firms

\begin{figure}[htbp]
	\centering
	\includegraphics[width=20em]{pics/McKenzie2017_mgmtdispersion.png}
	\label{McKenzie(2017): Mgmt practices}
\end{figure}

\vspace{-1.0em}

\begin{itemize_2pt}
	\item Heterogeneity in business practices across micro and small enterprises \citep{McKenzie2017}
\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Characterization of Business Practices}

Set of general best practices for small firms

\begin{itemize_2pt}
	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance

	\begin{itemize_2pt}	
	\vspace{0.5em}

		\item Validated in \textcolor{bdf}{7 countries} in Asia, Africa, and South America

		\item \textcolor{bdf}{4 major domains} of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}

@@

		\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} at one-year endline ($r=0.59$)
	\end{itemize_2pt}

\begin{frame}
\frametitle{Characterization of Business Practices}

\begin{itemize_2pt}
	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance

	\begin{itemize_2pt}	
	\vspace{0.5em}

		\item Example practices:

		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g.,  
		\end{enumerate_2pt}

\item[] $\rightarrow$ How exactly should we think about business practices translating into performance gains?

@@

		\begin{itemize_2pt}
			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
			\item[] .. where $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, $\textcolor{red}{r}$ cost of capital, and $\textcolor{red}{p}$ is the output price
			\item[] .. where $\textcolor{red}{A}$ represents a productivity factor and \textcolor{red}{$\lambda$} parameterizes borrowing constraints
		\end{itemize_2pt}

@@

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology boosting productivity factor $\textcolor{red}{A}$
			\item[] \citep[see,][]{Bloom2016, McKenzie2017, Quinn2019}
		\end{enumerate_2pt}

@@

Standard Production Decision
\begin{itemize_2pt}
	\item \tiny Owner maximizes output $Y = f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})$ at given wealth $\textcolor{red}{W}$:

	\item \normalsize Further specific channels of impact
	\begin{enumerate_2pt}
		\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
		\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013}
		\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand

		\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth
		\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
	\end{enumerate_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
	\item Correlation with productivity in mid-sized and large firms \citep{Bloom2019}
	\item \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms \citep{McKenzie2017}
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2021})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity

@@

\begin{frame}
\frametitle{Typical Training Program}
	Demand for business training

	\begin{figure}[htbp]
	\centering
	\includegraphics[width=17em]{pics/Maffioli2020_demand.png}
	\label{Maffioli(2020): Demand}
\end{figure}

	\begin{itemize_2pt}
	\item Demand curve for business training in Jamaica: $\sim$60-70\% willing to pay half, $\sim$10\% full price \citep{Maffioli2020}
	\end{itemize_2pt}
\end{frame}

@@

	Including more recent evaluations \citep[see,][]{McKenzie2021}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016, McKenziePuerto2021}
		\item ?
		\item More severe constraints, e.g., due to household-level reallocation \citep{Bernhardt2019, deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

Typical Consulting Intervention
\begin{itemize_2pt}
	\item Three-step procedure
	\begin{enumerate_2pt}
		\item Diagnosing practices
		\item Identifying areas of improvement
		\item Joint and interactive problem solving
	\end{enumerate_2pt}

@@

	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically $\sim$10\%) \\
	\begin{itemize_2pt}
		%\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_2pt}
	\item McKenzie cash JDE paper
	\item \citep{Gine2021}
	\item \cite{Berge2015}
	\item \cite{deMel2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\subsection{Measuring Firm Performance}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=23.5em]{pics/McK2020_profits.png}
		\label{McKenzie(2020): Profits2}
	\end{figure}

@@

	\begin{itemize_2pt}
		\item \textcolor{bdf}{Extremely wide confidence intervals} on impact estimates
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Self-reports and aggregation}

\citep{Garlick2019}
\citep{deMel2009}
\citep{Bernhardt2019}

@@

\appendix
\begin{frame}[label=references, allowframebreaks]
\frametitle{References}
\bibliographystyle{chicago}
\bibliography{businessTraining}
\end{frame}
